DMTN: Dual-Attention Multi-Task Network for Precise Spatio-Temporal Event Spotting in Volleyball Videos\\

### 2024-11-01 paper.tex
add fig for model arch [30% complete]
full model arch diagram

\section{Related work}

\subsection{Video Classification}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics{figures/fig1.png}}
    \caption{Model architecture.}
    \label{fig}
\end{figure}

>>>>

\section{Related work}
% TODO: Can write about Squeeze Ex and Multihead attention and their use in video understanding instead of TAL, etc... (or at least shorten them)
\subsection{Video Classification}

@@

\begin{figure*} 
    \centering
    \includegraphics[width=\textwidth]{figures/fig-arch.jpg}
    \caption{Illustration of DMTN Architecture Comprising Three Key Components: (1) \textbf{Feature Extractor} that processes each frame through RegNet-Y with Gate Shift Modules (GSM) to capture both spatial and temporal information; (2) \textbf{Dual-Attention Feature Aggregator} that combines Channel Attention and Temporal Attention mechanisms to integrate local and global spatio-temporal features, enhancing the model’s ability to capture subtle event dynamics; and (3) \textbf{Multi-Task Prediction Heads} that output per-frame classifications and spatial coordinates, enabling precise spatio-temporal event spotting for volleyball gameplay analysis.}    \label{fig-arch}
\end{figure*}
